---
title: "03 Automated Machine Learning with H20 ONE and TWO"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# Libraries

Load the following libraries. 

```{r}
library(h2o)
library(tidyverse)
library(readxl)
library(skimr)
library(GGally)
library(rsample)
library(recipes)
library(PerformanceAnalytics)  # for skewers
library(rpart.plot)
```


# Challenge

```{r}
 employee_attrition_tbl <- read_csv("datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")
```

## Helper function

```{r}
plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
#   
  color_expr <- enquo(color)
   
   if (rlang::quo_is_null(color_expr)) {
     
     g <- data %>%
       ggpairs(lower = "blank") 
     
   } else {
     
     color_name <- quo_name(color_expr)
     
     g <- data %>%
       ggpairs(mapping = aes_string(color = color_name), 
               lower = "blank", legend = 1,
               diag = list(continuous = wrap("densityDiag", 
                                             alpha = density_alpha))) +
       theme(legend.position = "bottom")
   }
   
   return(g)
   
}
  
```

## Number One
```{r}

employee_attrition_tbl %>%
  select(Attrition, contains("income")) %>%
  plot_ggpairs(Attrition)

#The answer is C 
```

##Number Two

```{r}

employee_attrition_tbl %>%
  select(Attrition, contains("PercentSalaryHike")) %>%
  plot_ggpairs(Attrition)

#The answer is D
```

## Number Three

```{r}

employee_attrition_tbl %>%
  select(Attrition, contains("StockOptionLevel")) %>%
  plot_ggpairs(Attrition)

#The answer is B
```

## Number Four

```{r}


employee_attrition_tbl %>%
  select(Attrition, contains("EnvironmentSatisfaction")) %>%
  plot_ggpairs(Attrition)

#The answer is A
```

## Number Five

```{r}


employee_attrition_tbl %>%
  select(Attrition, contains("WorkLifeBalance")) %>%
  plot_ggpairs(Attrition)

#The answer is B
```

## Number Six

```{r}


employee_attrition_tbl %>%
  select(Attrition, contains("JobInvolvement")) %>%
  plot_ggpairs(Attrition)

#The answer is A
```

## Number Seven

```{r}


employee_attrition_tbl %>%
  select(Attrition, contains("OverTime")) %>%
  plot_ggpairs(Attrition)

#The answer is B
```

## Number Eight

```{r}


employee_attrition_tbl %>%
  select(Attrition, contains("TrainingTimesLastYear")) %>%
  plot_ggpairs(Attrition)

#The answer is B
```

## Number Nine

```{r}


employee_attrition_tbl %>%
  select(Attrition, contains("YearsAtCompany")) %>%
  plot_ggpairs(Attrition)

#The answer is B
```

## Number Ten

```{r}

employee_attrition_tbl %>%
  select(Attrition, contains("YearsSinceLastPromotion")) %>%
  plot_ggpairs(Attrition)

#The answer is C
```

# Second challenge 

```{r}
product_backorders_tbl <- read_csv("product_backorders.csv")
```

## Split into test and train

```{r}
set.seed(seed = 1113)
split_obj <- rsample::initial_split(product_backorders_tbl, prop = 0.85)
```

## Assign training and test data

```{r}
train_readable_tbl<- training(split_obj)
test_readable_tbl <- testing(split_obj)
```

```{r}
  recipe_obj <- recipe( went_on_backorder~., data = train_readable_tbl) %>% 
  step_zv(all_predictors()) %>%
  prep()
  
train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)
```

## set the predictor names
```{r} 
 predictors <- c("national_inv", "lead_time", "forecast_3_month", "sales_3_month")
  
##specify the response

 response <- "went_on_backorder"
 h2o.init()
``` 

## Split data into a training and a validation data frame

```{r}
 # Setting the seed is just for reproducability
 split_h2o <- h2o.splitFrame(as.h2o(train_tbl), ratios = c(0.85), seed = 1234)
 train_h2o <- split_h2o[[1]]
 valid_h2o <- split_h2o[[2]]
 test_h2o  <- as.h2o(test_tbl)
```
 
## Set the target and predictors

```{r}
 y <- response
 x <- setdiff(names(train_h2o), y)
 
 
 automl_models_h2o <- h2o.automl(
   x = x,
   y = y,
   training_frame    = train_h2o,
   validation_frame  = valid_h2o,
   leaderboard_frame = test_h2o,
   max_runtime_secs  = 15,
   nfolds            = 5 
 )
```

## Prepare model

```{r}
 automl_models_h2o@leaderboard
 Model<-automl_models_h2o@leader
 h2o.saveModel(Model,path = "ml_journal-Automated_Machine_learning_2_model")
```